\documentclass[11pt]{article}  % need to compile twice
\usepackage{amsmath, textcomp, amssymb, geometry, graphicx, enumerate, ctex, float, multirow}
\usepackage[colorlinks, linkcolor=black]{hyperref}
\usepackage[table,xcdraw]{xcolor}

\geometry{left=2.54cm, right=2.54cm, top=3.18cm, bottom=3.18cm}

\def\Name{杨豪\space}  % Your name
\def\SID{2206213297}  % Your student ID number

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% need to be confirmed before each time writing and committing 
\def\Homework{15} % Number of Homework
\def\Session{2022-Fall}
\def\CourseCodeName{SOFT400127: Computer Organization and Architecture}
\def\simCourseName{OA}

\title{\vspace{-4cm}\CourseCodeName \space
        \Session \protect\\  Homework-~\textbf{\Homework} Solutions}
\author{软件2101 \Name \space 学号: \SID}
\markright{\simCourseName\ \space \Session\  HW-\Homework\ \Name}
\date{\today}


\begin{document}
\maketitle

~\textbf{Honor Code: I promise that I finished the homework solutions on my own without copying other people's 
    work.}
    
\section*{Instruction Level Parallelism and Superscalar Processors}

\subsection*{1. }

\begin{table}[H]
    \begin{tabular}{|c|c|c|}
    \hline
    \textbf{时钟} & \textbf{功能}  & \textbf{有效控制信号}  \\ \hline
    C5          & MAR←(R1)     & R1out, MARin     \\ \hline
    C6          & MDR←M(MAR)   & MemR, MDRinE     \\ \hline
    C7          & A←(MDR)      & MDRout, Ain      \\ \hline
    C8          & AC←(A)+(R0)  & R0out, Add, ACin \\ \hline
    C9          & MDR←(AC)     & ACout, MDRin     \\ \hline
    C10         & M(MAR)←(MDR) & MDRoutE, MemW    \\ \hline
    \end{tabular}
\end{table}

\subsection*{2. }

\subsubsection*{1). }

\begin{enumerate}[a.]
    \item MBR
    \item IR
    \item MAR
    \item PC
\end{enumerate}

\subsubsection*{2). }

PC→MAR→Main Memory→MBR→IR

\subsubsection*{3). }

\begin{itemize}
    \item Read: IR→MAR→Main Memory→MBR→AC→ALU
    \item Write: 
    \begin{enumerate}
        \item IR→MAR
        \item AC→MBR→Main Memory
    \end{enumerate}
\end{itemize}

\section*{Other things}

\begin{itemize}
    \item \LaTeX \space code refer to these things and was complied on texlive2020. 
    \begin{itemize}
        \item  \href{https://www.eecs70.org/assets/misc/homework_template.tex}{UCB-CS70's given homework template.} 
        \item  \href{https://www.latexlive.com}{A free website useful to edit \LaTeX \space formula code.}
    \end{itemize}
    \item Some context refer to Professor Li.~'s PPT.
\end{itemize}

The purpose of writing in English is to adapt to bilingual teaching and to improve my poor English 
writing skills in preparation for a possible future exchange program. 

    Thanks for your correcting and grading :).

\end{document}