\documentclass[11pt]{article}  % need to compile twice
\usepackage{amsmath, textcomp, amssymb, geometry, graphicx, enumerate, ctex, float, multirow}
\usepackage[colorlinks, linkcolor=black]{hyperref}
\usepackage[table,xcdraw]{xcolor}

\geometry{left=2.54cm, right=2.54cm, top=3.18cm, bottom=3.18cm}

\def\Name{杨豪\space}  % Your name
\def\SID{2206213297}  % Your student ID number

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% need to be confirmed before each time writing and committing 
\def\Homework{12} % Number of Homework
\def\Session{2022-Fall}
\def\CourseCodeName{SOFT400127: Computer Organization and Architecture}
\def\simCourseName{OA}

\title{\vspace{-4cm}\CourseCodeName \space
        \Session \protect\\  Homework-~\textbf{\Homework} Solutions}
\author{软件2101 \Name \space 学号: \SID}
\markright{\simCourseName\ \space \Session\  HW-\Homework\ \Name}
\date{\today}


\begin{document}
\maketitle

~\textbf{Honor Code: I promise that I finished the homework solutions on my own without copying other people's 
    work.}
    
\section*{Instruction Level Parallelism and Superscalar Processors}

\subsection*{1. }

\begin{itemize}
    \item true data dependency
    \item procedural dependency
    \item resource conflict
    \item output dependency
    \item antidependency
\end{itemize}

\subsection*{2. }

\begin{itemize}
    \item I1\&I2, true data dependency(R1)
    \item I2\&I3, output dependency(R2), output dependency(R2), antidependency(R2)
    \item I3\&I4, antidependency(R2)
\end{itemize}

solutions
\begin{itemize}
    \item true data dependency. Out of order or Insert irrelevant instructions.
    \item antidependency\&output dependency. Register renaming.
\end{itemize}


\section*{Other things}

\begin{itemize}
    \item \LaTeX \space code refer to these things and was complied on texlive2020. 
    \begin{itemize}
        \item  \href{https://www.eecs70.org/assets/misc/homework_template.tex}{UCB-CS70's given homework template.} 
        \item  \href{https://www.latexlive.com}{A free website useful to edit \LaTeX \space formula code.}
    \end{itemize}
    \item Some context refer to Professor Li.~'s PPT.
\end{itemize}

The purpose of writing in English is to adapt to bilingual teaching and to improve my poor English 
writing skills in preparation for a possible future exchange program. 

    Thanks for your correcting and grading :).

\end{document}